Validation of Visual Statistical Inference, with Application to Linear Models

### 2012-03-08 paper_jasa.tex
small changes

\subsection{Other methods to obtain power}

@@

\begin{equation}
g(\pi_{ij}) = X_{ij}B  + Z_{ij} \tau_j 
\label{mixed} 
\end{equation}
%
where $\tau_j$ is random effects coefficient vector of length $q$ for subject $j$,  $\tau_j  \sim  MVN(0,\Sigma)$ with variance covariance matrix $\Sigma$, $Z_{ij}$ is the $i$th row vector of random effects covariates for subject $j$, $B$ is a vector of coefficient of length $p$, the number of fixed effect covariates being used, $X_{ij}$ is the $i$th row vector of the fixed effects covariates for subject $j$ and link function $g(\mu)=log(\frac{\mu}{1-\mu}); 0 \le \mu \le 1$. The covariates could be demographic information of people such as age, gender, education level etc. as well as sample size ($n$), regression parameter ($\beta$) and variance ($\sigma^2$) of model \ref{multi}.

>>>>

\subsection{Estimating Power from Lineups}

@@

\begin{equation}
g(\pi_{ij}) = X_{ij}B  + Z_{ij} \tau_j 
\label{mixed} 
\end{equation}
%
where $\tau_j$ is random effects coefficient vector of length $q$ for subject $j$,  $\tau_j  \sim  MVN(0,\Sigma)$ with variance covariance matrix $\Sigma$, $Z_{ij}$ is the $i$th row vector of random effects covariates for subject $j$, $B$ is a vector of coefficient of length $p$, the number of fixed effect covariates being used, $X_{ij}$ is the $i$th row vector of the fixed effects covariates for subject $j$ and logit link function $g(\pi)=\log(\pi) - \log(1-\pi); 0 \le \pi \le 1$. The covariates could be demographic information of people such as age, gender, education level etc. as well as sample size ($n$), regression parameter ($\beta$) and variance ($\sigma^2$) of model \ref{multi}.
